\section{Week Structure}
In this section, we will describe the time table and weekly progress throughout the project. We will go over problems and some design decisions, especially those that had consequences for the overarching work flow.
\subsection{Time Table}
This time table reflects who took responsibility of what tasks. The table itself was developed without any assignment of responsibilities before beginning the project.
\begin{table}[h]
	\begin{tabular}{|l|l|l|}
		\hline
		Week number & Task & Owner\\
		\hline
		31-10-2015 & 4D-Movement & Both\\ 
		& Colour switching & Alex\\
		& Pickupable Objects & Emil\\
		\hline
		7-11-2015 & Composite objects, tuning of carrying implementation & Emil\\
		& Interactive objects & Alex\\
		\hline
		14-11-2015 & AI, Hazards and In-game displays & Both\\
		\hline
		21-11-2015 & Doors and locks, Refactoring of code & Alex\\
		& Elevator, level design & Emil\\
		\hline
		28-11-2015 & 4D-lighting, sound effects & Alex\\
		\hline
	\end{tabular}
	\caption{Work schedule separated into weeks}
	\label{tabWeek}
\end{table}

\subsection{Breakdown}
\subsubsection{Week one}
Initially, we needed to decide upon what approach to take in regards to the core mechanics of our game. Using the standard asset 'FPSController' shipping with Unity, we only needed a way to explore the fourth dimension. We figured that this movement would take on either of two possibilities; integral or fluid.\\

To better explore these possibilities, Emil started working with the integral approach, while Alex explored the fluid approach.\\

Our efforts revealed that a fluid approach would be much more faithful to the mathematical concept of dimensional movement, but would be exceedingly complicated to implement properly in the Unity engine, since the collision detection is handled by Unity behind the scenes. Fluid 4D-movement would require the collision detection system to be extended with a fourth coordinate, which was simply not feasible.\\

On the other hand, integral movement - being the more 'unrealistic' approach - would be much easier to implement even without compromising the core idea of the game. Additionally, it complimented the collision detection system of Unity through the use of collision layers, which with little interpretation could be transformed into a working 4D-collision engine.\\

With the movement system in place, Emil implemented the first version of pickupable objects, inspired by unitylessons.com\cite{unityLessons}. Meanwhile, Alex implemented the first version of the colour switching algorithms.

\subsubsection{Week two}
During the second week, we started working with especially composite objects; objects that stretched across multiple collision layers (had a w-width larger than 1). These objects proved to become a problem, given that they seemingly did not follow the laws of physics, detaching from each other seemingly at random.\\

Investigating, we concluded that this was a problem founded in our PickupObject script[citation needed], where we forced the displacement of carried objects instead of applying forces to it, hence bypassing the inherent physics inside Unity. This problem also meant that objects could displace through walls. Emil began solving these issues, while Alex started working with interactive elements, such as buttons.\\

Multiple problems were fixed during the week, with both issues related to PickupObject being solved. Button functionality was also added to the code. Regrettably a new problem appeared, where carried objects started floating around the player erratically, increasing in speed as it went. This problem was solved later in the process.\\

In the end, composite objects achieved a working state. While they did carry some complexity during implementation, their behaviour was reasonable.

\subsubsection{Week three}
With most of our core functionality implemented, we made an attempt to implement a simple AI and in-game monitors.\\

The AI was thought to be used as an opponent, but was never fully implemented to fulfil this position. Likewise, the in-game monitors were thought to relay information that was not obviously available to the player.\\

Due to misunderstandings, we thought the week to be imminently before feature freeze and focused our efforts implementing whatever features we found was still lacking. This reasoning was of course flawed, since we had no need for neither an AI or in-game monitors, and these never appeared in the final product.\\

The implementation of these minor, irrelevant features took time away from refactoring of our currently implemented code, which could have spared us many troubles later in the development.

\subsubsection{Week four}
Having gathered all of the features we deemed necessary, we started this week by distributing work between us. Alex became responsible for refactoring all of the currently available code, additionally creating the first implementation of the doors and locks that would later be used. Emil switched focus, and started development of content and designing levels, and was responsible for implementing the first elevator used in the game.\\

This week was undoubtedly the worst in work flow, and arguably catastrophic for the end result.\\

Given that the code implementation up until this point had been very specific as to its use, most of the refactoring was concerned with making the code more generic and easily accessible for the designers. Yet unintentionally, the refactoring created a multitude of new problems, breaking all of the previous functionality and thereby rendering most of the code useless. While it did fulfil its purpose regarding core functionality, many tangential features were utterly useless after the refactoring, e.g. the elevator and socketing system were broken, and buttons were volatile.\\

Upon realizing the situation, we decided to start fixing a multitude of problems, eventually resulting in working, albeit unstable, code. The fixes included correctly rendering trees and bushes, reimplementing pickupables and inventory items, fixing interaction between multiple 4D-objects, adding additional algorithms for animated doors and similar objects, and fixing the floating of carried objects.

\subsubsection{Week five}
While our time table suggested that we were to add 4D-lighting and sound effects, most of the fifth week went by with content creation and bug fixing.